---
title: "nonpareil_prediction_example"
author: "Jiaxian_Shen"
date: "9/27/2021"
output: html_document
---

# Introduction
This script is an example of using nonpareil package to predict coverage by sequencing effort, or vice versa, given that diversity is known.

# Steps
1. Get the Nonpareil diversity (or diversity range) from the machine learning model
2. Select several samples from the dataset representing the diversity (or diversity range)
3. Follow the below scripts  to get the predictions (target coverage -> sequencing effort ; seq effort -> estimated coverage)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Libraries ----
library(dplyr)  
library(Nonpareil)
```


```{r}
# Predict coverage by sequencing effort and diversity----
np_example <- Nonpareil.curve('example.npo')
coverage <- predict(np_example,1.711330e+08)   # 1.711330e+08 is an example of the sequencing effort

# get sequencing effort by targeted coverage and diversity----
pa <- coef(np_example$model)[1]
pb <- coef(np_example$model)[2]

LR_0.9 <- Nonpareil.antif(0.9, pa, pb)  # sequencing effort at 90% coverage
# note that the above operations only work for Formal class 'Nonpareil.Curve', not work for Formal class 'Nonpareil.Set'
```




